---
title: "Data Wrangling Assessment Task 2: Creating and pre-processing synthetic data"
author: "Insert student name and number here"
subtitle: 
output: 
  word_document: default
  html_document:
    df_print: paged
  html_notebook: default
---
If you have any questions regarding the assignment instructions and the R Markdown template, please post it on the discussion board **Questions on completing Assessment 2.**  


## Setup 

Insert and load the packages you need to produce the report here:
```{r}
# This is a chunk where you can load the packages required for producing the report

install.packages("tinytex")
```


## Instructions
Follow the instructions given in the Assessment brief to fill out the template below. Remember to include R codes and outputs and explain your working and results in plain text.


## Data Description 

Write your plain text here. 

You may use a bullet list like this: 

* bullet point 1
* bullet point 2
* ....


```{r}

# This is a chunk for creating your synthetic datasets. 
# Provide your R code here

```


## Merge

Write your plain text here.


```{r}

# This is a chunk for merging the datasets. 
# Provide your R code here

```


## Understand 

Write your plain text here.


```{r}

# This is a chunk where you inspect the types of variables, data structures, check the attributes in the data and apply proper data type conversions

```



##	Manipulate Data 

Write your plain text here.


```{r}

# This is a chunk where you create/mutate at least one variable from existing variables

```

##	Scan I 

Write your plain text here.


```{r}

# This is a chunk where you scan the data for missing values.

```

##	Scan II

Write your plain text here.


```{r}

# This is a chunk where you scan the numeric data for outliers. 

```


##	Transform 

Write your plain text here.


```{r}

# This is a chunk where you apply an appropriate transformation to at least one of the variables.

```


## Summary statistics

Write your plain text here.


```{r}

# This is a chunk where you produce summary statistics.

```



<br>
<br>
